Type Refinements for the Working Class

### 2015-11-12 paper.tex
Typo
Remove resolved TODO
Add a header
I think we need the right kan extension here (?)
@freebroccolo Is this right? The intention was to take the limit of the
diagram (that is, the product of the family).
fix some typos

Then, for any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework. Recall from \cite{sterling-morrison:2015}
that $\SCtx$ is the category of symbol-contexts and their injective,
sort-preserving renamings. Then, fix a small category $\mathcal{W}$ of worlds
along with a map $\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ such that
$\pi_\mathcal{W}$ is a Grothendieck opfibration. Then, a \emph{judgment} shall
be interpreted as an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$; in other words, a judgment is
identified with the intensional set of its renaming-sensitive derivations.

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as follows:
  \[
    \Define{{\square\Omega}}{
      \prod_{(\MV{m}:v)\in\Omega}
        \MkSet{E\mid\IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
    }
  \]

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Lan_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

@@

\subsection{Functional Refinement and Equality}

@@

\todo[inline]{%
  Properly express the \emph{syntactic} presuppositions of the sequent
  judgments so that the use of hypothetical and general judgment is
  well-formed.
}

@@

@@

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\psi}{\Gamma}{\sigma}$,
where $\RefinesCtx{\Phi}{\Upsilon}$.
\[
  \infer{
    \HRMemEq{\Phi}{\Psi,x:\psi}{M}{N}{\phi}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{\MV{m},\MV{n}:\sigma}{
      \HypJ{
        \HRMemEq{\Phi}{\Psi}{
          \Subst{\MV{m}}{x}{\phi}
        }{
          \Subst{\MV{n}}{x}{\psi}
        }{\phi}
      }{
        \HRMemEq{\Phi}{\Psi}{\MV{n}}{\MV{n}}{\psi}
      }
    }
  }
\]

>>>>

Then, for any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework. Recall from \cite{sterling-morrison:2015}
that $\SCtx$ is the category of symbol-contexts and their injective,
sort-preserving renamings. Then, fix a small category $\mathcal{W}$ of worlds
along with a map $\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ such that
$\pi_\mathcal{W}$ is a Grothendieck fibration. Then, a \emph{judgment} shall
be interpreted as an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a judgment
is identified with the intensional set of its renaming-sensitive derivations.

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as follows:
  \[
    \Define{{\square\Omega}}{
      \prod_{(\MV{m}:v)\in\Omega}
        \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Ran_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

@@

\subsection{Functional Refinement}

@@

@@

\subsection{Functional Equality}

@@

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\psi}{\Gamma}{\sigma}$,
where $\RefinesCtx{\Phi}{\Upsilon}$.
\[
  \infer{
    \HRMemEq{\Phi}{\Psi,x:\psi}{M}{N}{\phi}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{\MV{m},\MV{n}:\sigma}{
      \HypJ{
        \HRMemEq{\Phi}{\Psi}{
          \Subst{\MV{m}}{x}{\phi}
        }{
          \Subst{\MV{n}}{x}{\psi}
        }{\phi}
      }{
        \HRMemEq{\Phi}{\Psi}{\MV{m}}{\MV{n}}{\psi}
      }
    }
  }
\]
